On Combinatorial Games and de Bruijn Sequences

### 2016-10-27 infdebruijn.tex
aaa
.

\begin{proposition}
	\label{hat-w-at-the-tail}
	For any $w=0^l \sigma \hat{w}\in L_n$ where $\sigma$ is a non-zero letter and $\hat{w}$ is a non-empty word there is a non-empty word $u$ such that $b(w)=u\hat{w}$.
\end{proposition}
\begin{proof}
	If $|w|\neq n$ the proof follows by Proposition~\ref{w-at-the-tail}. If $|w|=n$ then $b_1(w)=w$, $b_2(b_1(w))=\sigma\hat{w}$, and $b_3(b_2(b_1(w)))=(\sigma-1)\hat{w}$ and the claim follows as well.
\end{proof}

\begin{proposition}
	\label{tail-is-preserved*}
	For any $w=0^l \sigma \hat{w}\in L_n$ where $\sigma$ is a non-zero letter and $\hat{w}$ is a non-empty word there is a non-empty word $u$ such that $b^*(w)=u\hat{w}$.
\end{proposition}
\begin{proof}
By definition, $b^*$ consists of repeated applications of $b$ until a word whose length devides $n$ is obtained. In particular, only the first of these applications of $b$ act on a parameter whose length may be $n$. By Proposition~\ref{hat-w-at-the-tail}, this first application produces a word that ends with $\hat{w}$ and by Proposition~\ref{w-at-the-tail} each of the remaining applications only add prefixes. 
\end{proof}

>>>>

\begin{proposition}
	\label{hat-w-at-the-tail}
	For any $w=0^l \sigma \hat{w}\in L_n$ where $\sigma$ is a non-zero letter there is a non-empty word $u$ such that $b(w)=u\hat{w}$.
\end{proposition}
\begin{proof}
	If $|w|\neq n$ the proof follows by Proposition~\ref{w-at-the-tail}. If $|w|=n$ then $b_1(w)=w$, $b_2(b_1(w))=\sigma\hat{w}$, and $b_3(b_2(b_1(w)))=(\sigma-1)\hat{w}$ and the claim follows as well.
\end{proof}
